Operation Mode Study in Cloud Manufacturing Ecosystem

### 2016-11-01 Response.tex

Thank you for the suggestion. I've changed the Fig. 1 into parallel style that enlarges the words in this figure, I've also redrawn Fig. 2 and Fig. 1 with \textit{MS Visio} so that they are more crisp now. All the figures now are vectorgraphs.

\section*{Review 2's comment} % (fold)  
The authors should get in touch with the study's relevance with the environmental issues. Otherwise, the article's relevance with the conference is regarded to be low.
I would recommend the authors to describe the 3 modes (incubation, outsourcing, and metabolism modes) so that the readers can understand them more easily.

\textbf{Response:}

Thank you for your suggestion. Previous manuscript considered environmental issues in the view of the life cycle vicissitude of resource in cloud manufacturing, so we designed bunches of operation modes to study how to optimize the manufacturing resources for the overall industry. I must admit that these contents are not obvious enough, so apart from changing the representations, I also add a section (2.1 Background) to describe the environmental issues with regard to cloud manufacturing. Additional simpler description of the proposed 3 modes are add to 3.4, 3.5, 3.6 respectively, and I also simplified the description of the original mode in 3.3.
\end{document}

### 2016-11-01 design.tex
clearify what to change

    $\bm{mr}_l$ & Resource member set of $ms_l$\\
    $\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\

@@

    $\bm{\alpha}_l$ & Subset of $\bm{q}_l$ that consists of all the capacities of type $\alpha$ resources in $\bm{mr}_l$\\

@@

    $\bm{x}$ & Bold font of the variable($x$) means the temp set of a bunch of these variables\\

@@

% \subsubsection{Demander select from resource candidates}
% \label{subs:select_resource_candidates}
A demander makes decision about resource selection from $\mathcal{R}_{ij,\tau}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$. Without loss of generality, we suppose at time $\tau \ge r_i$, the decision-making of demander can be described as follows,
% \begin{equation}
% \max_{\forall \bm{k}}\left( \delta_{\bm{k}},
% R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
% \right) \label{eq:selectresaim}
% \end{equation}
% \begin{numcases}{\text{s.t.}}
% q_{\alpha,ij} \le C_{k_{\alpha},\tau} & $\alpha\in\mathcal{A}_{ij}$\label{eq:rescaplimit}\\
% \mathcal{R}_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & $\alpha\in\mathcal{A}_{ij}$\label{eq:restypeabstract}\\
% \mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \label{eq:nrc}\\
% \bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right] & \label{eq:decisionvectork}\\
% k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &$\alpha\in\mathcal{A}_{ij}$ \label{eq:decisionvark}
% \end{numcases}

The multi-objective in \autoref{eq:selectresaim} aims at high quality, high resource owner rank and low waiting queue length. \autoref{eq:rescaplimit} ensures that resource capacity is capable to process the task-part, \autoref{eq:restypeabstract}--\ref{eq:nrc} restrict the resource candidates' type in the task configuration, \autoref{eq:decisionvectork}--\ref{eq:decisionvark} describe decision variables, the demander should make decision to select resources in each type.

@@

\subsection{Incubation mode} % (fold)
\label{sub:incubation_mode}
Incubation mode is one extension for the original mode, the purpose of this mode is to remove the cooperation and assembly procedure in advance by gathering types of resources with certain quota into manufacturing service, which will be incubated as shown in incubation part of \autoref{fig:modes}.
% \begin{figure}[htbp]
%     \centering
%     \resizebox{0.7\textwidth}{!}{\input{figures/service-incubate}}
%     \caption{Incubation mode}
%     \label{fig:serviceincubatemode}
% \end{figure}
\begin{figure}[htbp]
    \centering
    \scriptsize
    \resizebox{.65\textwidth}{!}{\input{figures/service}}
    \caption{Service incubation from $job_7$ in \autoref{tab:simplejobconfiguration}}
    \label{fig:servicefigure}
\end{figure}
After the finish of task-part, provider record the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such a task-specified service for the future performance. As the example in \autoref{fig:servicefigure}, if task $job_1$ in \autoref{tab:simplejobconfiguration} was finished, the first thing of incubation for the resource provider is to publish a job named \textbf{service-call} ($job_7$), which is similar to task except for the capacity dominance feature , which means capacity of selected resource will not be restored after the processing. The process result of one service-call is manufacturing \textbf{service} as shown in \autoref{fig:servicefigure}, which is actually a set of resources that may come from selected providers in the system, it's possible for more than one resources in a same type to make contributions to the incubation of one service. No more cooperation and assembly procedure are one pro of service, and product quality will no longer be restricted to the worst quality of resources for the complementary effect, while one con of service include that service can only perform specified task.
Now we can generalize task and service-call into \textbf{job}, resource and service into \textbf{machine} for the follow discuss.

@@

\resume{asparaenum}
\item Select behavior
\suspend{asparaenum}
Apart from the condition that $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}=0$, provider of $sc_l$ will select $mr_k$ when $\mathcal{B}_{l,\tau}\subset\mathcal{A}_l$, and the difference is that the $\bm{l}_{\alpha}$ (subset of decision variable $\bm{l}$) here is also a set of selected resources with type $\alpha$. Capacities of selected resources will be changed, and if the sum of capacity value in $\bm{l}_{\alpha}$ is less than the value $sc_l$ required, this selection will not to be executed.
% \begin{subnumcases}{}
% C_{k,\tau} := C_{k,\tau} - q_{\alpha,l}& If $C_{k,\tau} \ge q_{\alpha,l}$\label{eq:capq}\\
% C_{k,\tau} := 0 & otherwise \label{eq:cap0}
% \end{subnumcases}
Demander of $t_{ij}$ will select $ms_l$ when $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}>0$ and this implies that the resource candidates are not enough and there exists service candidates.

% \begin{equation}
% \max_{\forall l}\left( \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)\label{eq:selectserviceaim}
% \end{equation}
% \begin{numcases}{\text{s.t.}}
% \Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \label{eq:servicecomplydist}\\
% \mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
% \sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \label{eq:servicecomplydistend}\\
% l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \label{eq:decisionvariablel}
% \end{numcases}
Similar to \autoref{eq:selectresaim}, \autoref{eq:selectserviceaim} is also a multi-objective function that aims at high quality, high service owner rank and low job queue length. \autoref{eq:servicecomplydist}--\ref{eq:servicecomplydistend} explain the service quality distribution parameters, \autoref{eq:decisionvariablel} is the decision variable to select one service in $\mathcal{S}_{ij,\tau}$.

@@

Similar to other situations, \autoref{eq:combaim} is a multi-objective function that aims at high quality, high rank and low waiting queue length. \autoref{eq:optk} and \autoref{eq:optl} are the optimal decision in independent conditions, \autoref{eq:temprank}, \autoref{eq:templength} and \autoref{eq:tempqualitystart} are the virtual rank value, virtual queue length and virtual quality value that are set in the worst cases.\autoref{eq:tempqualitystart}--\ref{eq:tempqualityend} are the virtual quality value calculation procedure. \autoref{eq:newdicisionvariable} is the decision to choose one of these two partial optimal decision.

@@

\begin{figure}[htbp]
	\centering
	\large
	\resizebox{.95\textwidth}{!}{\input{figures/scheduleChart}}
	\caption{Simple instance schedule chart with 4 resources in 3 different types}
	\label{fig:scheduleChart}
\end{figure}

In every single resource, a schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{(s)}_n\right]$,$n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}}$. Even though provider will not schedule $job_\theta\in\mathcal{H}_{k,\tau_0}$, the finish time $f_\theta$ of these job cannot be determined because the waiting in the cooperation. We ignore the type subscript $\alpha$ because all the job assigned here are already type-matched. The schedule model is:

>>>>

    % $\bm{mr}_l$ & Resource member set of $ms_l$\\
    % $\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\

@@

    % $\bm{\alpha}_l$ & Subset of $\bm{q}_l$ that consists of all the capacities of type $\alpha$ resources in $\bm{mr}_l$\\

@@

    % $\bm{x}$ & Bold font of the variable($x$) means the temp set of a bunch of these variables\\

@@

% \subsubsection{Demander select from resource candidates}
% \label{subs:select_resource_candidates}
A demander makes decision about resource selection from $\mathcal{R}_{ij,\tau}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$. Without loss of generality, we suppose at time $\tau \ge r_i$,
the decision-making of demander can be formulated as the special case of general model, which aims at multi-objective function as \autoref{eq:optk}.
% \begin{equation}
% \max_{\forall \bm{k}}\left( \delta_{\bm{k}},
% R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
% \right) \label{eq:selectresaim}
% \end{equation}
% \begin{numcases}{\text{s.t.}}
% q_{\alpha,ij} \le C_{k_{\alpha},\tau} & $\alpha\in\mathcal{A}_{ij}$\label{eq:rescaplimit}\\
% \mathcal{R}_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & $\alpha\in\mathcal{A}_{ij}$\label{eq:restypeabstract}\\
% \mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \label{eq:nrc}\\
% \bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right] & \label{eq:decisionvectork}\\
% k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &$\alpha\in\mathcal{A}_{ij}$ \label{eq:decisionvark}
% \end{numcases}

@@

\subsection{Incubation mode} % (fold)
\label{sub:incubation_mode}
Incubation mode is one extension for the original mode, the purpose of this mode is to remove the cooperation and assembly procedure in advance by gathering types of resources with certain quota into manufacturing service, which will be incubated as shown in incubation part of \autoref{fig:modes}.
% \begin{figure}[htbp]
%     \centering
%     \resizebox{0.7\textwidth}{!}{\input{figures/service-incubate}}
%     \caption{Incubation mode}
%     \label{fig:serviceincubatemode}
% \end{figure}
\begin{figure}[htbp]
    \centering
    \scriptsize
    \resizebox{.65\textwidth}{!}{\input{figures/service}}
    \caption{Service incubation from $job_7$ in \autoref{tab:simplejobconfiguration}}
    \label{fig:servicefigure}
\end{figure}
After the finish of task-part, provider record the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such a task-specified service for the future performance. As the example in \autoref{fig:servicefigure}, if task $job_1$ in \autoref{tab:simplejobconfiguration} was finished, the first thing of incubation for the resource provider is to publish a job named \textbf{service-call} ($job_7$), which is similar to task except for the capacity dominance feature, which means capacity of selected resource will not be restored after the processing. The process result of one service-call is manufacturing \textbf{service} as shown in \autoref{fig:servicefigure}, which is actually a set of resources that may come from selected providers in the system, it's possible for more than one resources in a same type to make contributions to the incubation of one service. No more cooperation and assembly procedure are one pro of service, and product quality will no longer be restricted to the worst quality of resources for the complementary effect, while one con of service include that service can only perform specified task.
Now we can generalize task and service-call into \textbf{job}, resource and service into \textbf{machine} for the follow discuss.

@@

\resume{asparaenum}
\item Select behavior
\suspend{asparaenum}
Apart from the condition that $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}=0$, provider of $sc_l$ will select $mr_k$ when $\mathcal{B}_{l,\tau}\subset\mathcal{A}_l$, and the difference is that the $\bm{l}_{\alpha}$ (subset of decision variable $\bm{l}$) here is also a set of selected resources with type $\alpha$. Capacities of selected resources will be changed, and if the sum of capacity value in $\bm{l}_{\alpha}$ is less than the value $sc_l$ required, this selection will not to be executed.
% \begin{subnumcases}{}
% C_{k,\tau} := C_{k,\tau} - q_{\alpha,l}& If $C_{k,\tau} \ge q_{\alpha,l}$\label{eq:capq}\\
% C_{k,\tau} := 0 & otherwise \label{eq:cap0}
% \end{subnumcases}
Demander of $t_{ij}$ will select $ms_l$ when $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}>0$ and this implies that the resource candidates are not enough and there exists service candidates.
This decision-making of demander can also be formulated as the special case of general model, which aims at multi-objective function as \autoref{eq:optl}.

% \begin{equation}
% \max_{\forall l}\left( \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)\label{eq:selectserviceaim}
% \end{equation}
% \begin{numcases}{\text{s.t.}}
% \Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \label{eq:servicecomplydist}\\
% \mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
% \sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \label{eq:servicecomplydistend}\\
% l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \label{eq:decisionvariablel}
% \end{numcases}

@@

% The multi-objective in \autoref{eq:selectresaim} aims at high quality, high resource owner rank and low waiting queue length. \autoref{eq:rescaplimit} ensures that resource capacity is capable to process the task-part, \autoref{eq:restypeabstract}--\ref{eq:nrc} restrict the resource candidates' type in the task configuration, \autoref{eq:decisionvectork}--\ref{eq:decisionvark} describe decision variables, the demander should make decision to select resources in each type.

% Similar to \autoref{eq:selectresaim}, \autoref{eq:selectserviceaim} is also a multi-objective function that aims at high quality, high service owner rank and low job queue length. \autoref{eq:servicecomplydist}--\ref{eq:servicecomplydistend} explain the service quality distribution parameters, \autoref{eq:decisionvariablel} is the decision variable to select one service in $\mathcal{S}_{ij,\tau}$.

The decision variable $\bm{k}$ is a vector that wraps $k_\alpha$ up ($\alpha\in\mathcal{A}_{ij}$). 
\autoref{eq:combaim} is a multi-objective function that aims at high quality, high rank and low waiting queue length. \autoref{eq:optk} and \autoref{eq:optl} are the optimal decision in independent conditions. \autoref{eq:temprank} determines the virtual rank value while \autoref{eq:templength} determines virtual queue length that are set in the worst cases.
% \autoref{eq:tempqualitystart}--\ref{eq:tempqualityend} are the virtual quality value calculation procedure.
\autoref{eq:newdicisionvariable} is the decision to choose one of these two partial optimal decision. The determination of $\Delta_{\bm{k}^*}$ is tedious and insignificant so that we are not going to show the details.

@@

\begin{figure}[htbp]
	\centering
	\large
	\resizebox{.9\textwidth}{!}{\input{figures/scheduleChart}}
	\caption{Simple instance schedule chart with 4 resources in 3 different types}
	\label{fig:scheduleChart}
\end{figure}

In every single resource, a schedule is given by a vector of ideal finish times $\bm{f}^{(s)}$ wraps $f^{(s)}_\theta$ up ($job_\theta\in\mathcal{L}^{(s)}_{k,\tau_0}$). Even though provider will not schedule $job_\theta\in\mathcal{H}_{k,\tau_0}$, the finish time $f_\theta$ of these job cannot be determined because the waiting in the cooperation. We ignore the type subscript $\alpha$ because all the job assigned here are already type-matched. The schedule model is:
